```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Object functions

Previously, we learned about some low-level functions that work with the environment and packages. In this section, we will get to know some basic functions that deal with objects in general.

## Typing

Although everything in R is an object, objects do have different types.

Suppose  the object we are dealing with is user-defined. We create a function that behaves in different ways according to the type of the input object. For example, we need to create a function named `takeit` that takes the first element if the input object is a atomic vector, but takes user-defined element if the input object is a list of data and index.

```{r}
takeit <- function(x) {
  if(is.atomic(x)) {
    x[1]
  } else if(is.list(x)) {
    x$data[[x$index]]
  }
}
```

The above function behaves differently as `x` takes different types. When `x` takes an atomic vector (e.g. numeric vector), the function extracts its first element; when `x` takes a list of `data` and `index`, the function extracts the element with index of `index` from `x$data`.

```{r}
takeit(c(1,2,3))
takeit(list(data=c(1,2,3),index=3))
```



```{r}
x <- 1
class(x)
typeof(x)
str(x)

x <- c(1,2,3)
class(x)
typeof(x)
str(x)

x <- c("a","b")
class(x)
typeof(x)
str(x)

x <- list(a=1,b=2)
class(x)
typeof(x)
str(x)

x <- data.frame(a=1,b=2)
class(x)
typeof(x)
str(x)
```

[summary table]

## Object dimensions

```{r}
df <- data.frame(a=c(1,2,3),b=c(2,3,4))
m1 <- matrix(c(1,2,3,2,3,4,3,4,5),ncol = 3)
a1 <- array(1:48,dim = c(2,8,3))
dim(df)
dim(m1)
dim(a1)
ncol(df)
nrow(df)
ncol(m1)
nrow(m1)
ncol(a1)
nrow(a1)
```

