```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Array

Array is a natural extension to matrix in its number of dimensions. More specifically, an array is a vector that is represented and accessible in a given number of dimensions. 

If you are already feel familiar with vectors and matrices, you won't be surprise to see anything that is applicable to arrays.

## Defining array

To define an array, we use `array` function by supplying a vector data, how these data are arranged in different dimensions, and sometimes the names of the rows and columns in these dimensions.

Suppose we have some data (10 integers from 0 to 9) and we need to arrange them in three dimensions: 1 for the first dimension, 5 for the second, and 2 for the third.

```{r}
a1 <- array(c(0,1,2,3,4,5,6,7,8,9),dim=c(1,5,2))
a1
```

We can clearly see how we may access these entries by looking at the notations around them.

Moreover, we can add names for these dimensions when create the array.

```{r}
a1 <- array(c(0,1,2,3,4,5,6,7,8,9),dim=c(1,5,2),
  dimnames=list(c("r1"),c("c1","c2","c3","c4","c5"),c("k1","k2")))
a1
```

Alternatively, for an array that is already created, we can call `dimnames(...) <-` to setup the names for each dimension by supplying a list of several character vectors.

```{r}
a0 <- array(c(0,1,2,3,4,5,6,7,8,9,10),dim=c(1,5,2))
dimnames(a0) <- list(c("r1"),c("c1","c2","c3","c4","c5"),c("k1","k2"))
a0
```

## Subsetting array

The principle of subsetting an array is exactly the same with subsetting a matrix. Here we can supply a vector for each dimension to extract a subset of an array.

```{r}
a1[1,,]
a1[,2,]
a1[,,1]
a1[1,1,1]
a1[1,2:4,1:2]
a1[c("r1"),c("c1","c3"),"k1"]
```

