```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Data frame

A data frame is a table with a number of rows and columns like a matrix. However, columns in a data frame need not be the same type. It is consistent with most data tables: different types of information describe a data record. 

The following example is a table that can be fully characterized by a data frame.

| Name     | Gender | Age | Major            |
|----------|--------|-----|------------------|
| Ken      | Male   | 24  | Finance          |
| Ashley   | Female | 25  | Statistics       |
| Jennifer | Female | 23  | Computer Science |

## Defining data frame

```{r}
data.frame(id=1:5,x=c(0,2,1,-1,-3),y=c(0.5,0.2,0.1,0.5,0.9))
data.frame(id=1:10,x=runif(10),y=rnorm(10))
data.frame(id=1:5,name=c("A","A","B","B","C"),x=runif(5),y=rnorm(5))
data.frame(id=1:5,name=c("A","A","B","B","C"),x=runif(5),y=rnorm(5),stringsAsFactor=FALSE)

df1 <- data.frame(1:5,c("A","A","B","B","C"),rnorm(5))
colnames(df1) <- c("id","name","x")
rownames(df1) <- letters[1:5]

as.data.frame(matrix(c(1,2,3,4,5,6,7,8,9),nrow=3,byrow=FALSE))
```


## Subsetting data frame

In essence, data frame is nothing special but a list of vectors, each of which contains the same number of elements. Therefore, it has common features of both list and matrix.

```{r}
df1$id
df1[1]
df1["name"]
df1[c("id","name")]
df1[1:2]
df1[,"name"]
df1[,c("name","x")]
df1[,1:2]
df1[1:4,]
df1[1:4,"x"]
df1[1:4,c("id","x")]
df1[df1$x>=0,]
df1[df1$name=="A",]
```

## Transforming a data frame

## Loading data frame from a file

## Saving data frame to a file
