```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# List

A list is a generic vector that is allowed to include different types of objects, even other lists.

## Defining list

We can use `list` function to define a list. Different types of objects can be put into one list. For example, the following code creates a list that contains a single-entry numeric vector, two-entry logical vector, and a character vector containing three values.

```{r}
l0 <- list(1,c(TRUE,FALSE),c("a","b","c"))
l0
```

We can assign names to each entry by using named arguments.

```{r}
l1 <- list(a=1,b=2,c=3)
l1
```



```{r}
l1$a
l1["a"]
l1[["a"]]
l1[c("a","b")]
names(l1) <- c("A","B","C")
l1$d <- 4
```

```{r}
l2 <- list(a=c(1,2,3),b=c("x","y","z","w"))
l2$b

is.list(l1)
as.list(c(1,2,3))
```

```{r}
l3 <- as.list(c(a=1,b=2,c=3))
l3$d
l3$d <- c("hello","world")
l3
```

```{r}
l4 <- list(a=1,b=2,c=3)
c4 <- unlist(l4)
l4 <- list(a=1,b=2,c="hello")
c4 <- unlist(l4)
```
