```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# List

A list is a generic vector that is allowed to include different types of objects, even other lists. 

It is useful for its flexibility. For example, a linear model fit in R is basically a list object that contains rich results of a linear regression such as linear coefficients (numeric vector), residuals (numeric vector), QR decomposition (a list containing a matrix and other objects), and so on. 

It is very handy to extract the information without calling different functions each time because these results are all packed into a list.

## Creating list

We can use `list` function to define it. Different types of objects can be put into one list. For example, the following code creates a list that contains a single-entry numeric vector, a two-entry logical vector, and a character vector of three values.

```{r}
l0 <- list(1,c(TRUE,FALSE),c("a","b","c"))
l0
```

We can assign names to each entry by using named arguments.

```{r}
l1 <- list(x=1,y=c(TRUE,FALSE),z=c("a","b","c"))
l1
```

## Extracting value from a list

There are various ways to access the members of a list. The most common way is using dollar-sign `$` to extract *the value* of a list member by name.

```{r}
l1$x
l1$y
l1$z
l1$m
```

Note that if we ask for a non-existing member `m`, its value is `NULL`.

Alternatively, we can supply a number `n` in double square brackets to extract the value of the n-th list member. For example, we can extract the value of the second member of list `l1`.

```{r}
l1[[2]]
```

With the same notation, we can also supply a name to extract the value of the list member with that name, just like using dollar sign.

```{r}
l1[["y"]]
```

It can be more flexible to use double square brackets from value extraction from a list, because sometimes we might not know which member we need to extract before some computation.

```{r}
member <- "z" # some more computation can happen here
l1[[member]]
```

Here we supply a runtime-evaluated, single-entry character vector to the brackets. But why should we use double brackets here? Where are the single brackets?

## Subsetting a list

In many cases we need to extract multiple members from a list. These multiple members also construct a list as a subset of the original list.

To subset a list, we can use single-square-bracket notation, just like what we use for vectors and matrices. We can extract the *members* of a list to put into a new list.

The notation is very much consistent with how it works for vectors. We can supply a character vector to extract members by name, a numeric vector by index, or a logical vector by indicating whether to select each of them.

```{r}
l1["x"]
l1[c("x","y")]
l1[1]
l1[c(1,2)]
l1[c(TRUE,FALSE,TRUE)]
```

## Naming list members

No matter whether the list members have already got names when they are defined, we can always name or rename the members in a list, just like how we do it with vectors.

```{r}
names(l1) <- c("A","B","C")
l1
```

To remove their names, we just assign `NULL` value to its names.

```{r}
names(l1) <- NULL
l1
```

but we can no longer access these members by name but by index and logical selection.

## Setting values

Setting the values in a list is as straightforward as how we work with vectors.

```{r}
l1 <- list(x=1,y=c(TRUE,FALSE),z=c("a","b","c"))
l1$x <- 0
```

If we assign a value to a non-existing member, we will add a new member to the list with that name or index.

```{r}
l1$m <- 4
l1
```

Also, we can set multiple values at the same time.

```{r}
l1[c("y","z")] <- list(y="new value for y",z=c(1,2))
l1
```


If we need to remove some of the members in a list, just assign `NULL` value to them.

```{r}
l1$x <- NULL
l1
l1[c("z","m")] <- NULL
l1
```


## Other functions

Many functions in R are related to list. For example, if we are not sure whether an object is a list or not, we can call `is.list` function to find out.

```{r}
l2 <- list(a=c(1,2,3),b=c("x","y","z","w"))
is.list(l1)
is.list(l1$a)
```

Here `l2` is a list but `l2$a` is a number vector rather than a list.

We can also convert a vector to a list by calling `as.list` function.

```{r}
l3 <- as.list(c(a=1,b=2,c=3))
l3
```

It is also very easy to coerce a list to a vector by calling `unlist` that basically converts all list members and put them to a vector of a commonly tolerable type.

```{r}
l4 <- list(a=1,b=2,c=3)
unlist(l4)
```

If we unlist a list of numbers and texts in mixture, all members will be converted to the closest type that each one can be converted to.

```{r}
l4 <- list(a=1,b=2,c="hello")
unlist(l4)
```

Here `a` and `b` are numbers and can be converted to character but `c` is a character vector cannot be validly convert to numbers. Therefore, their closest type that tolerates all members is character vector.

## rlist package

I created a package named `rlist`. It is a set of functions that make it easier to work with lists especially when they are used to store data in flexible structures. We will introduce this package in detail in the chapter of packages. You can visit its [website](http://renkun.me/rlist), see its page on [CRAN](http://cran.r-project.org/web/packages/rlist/), or view this project on [GitHub](https://github.com/renkun-ken/rlist).
