```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here

```

# Vector

A vector is a group of primitive objects of the same type. It is one of the building blocks of R objects. 

There are several types of vectors in R. They distinct from each other in the type of entries they hold. Here we will see the most commonly used types of vectors including numeric vector, logical vector, character vector, and so on.


#### Numeric vector

There are various ways to define a numeric vector.

A scalar number is the simplest numeric vector in R. It's only special in that its length is one.

```{r}
1.5
```

We can call `numeric` function to create a zero vector of a specific length.

```{r}
numeric(10)
```

We can also use `c` function to *combine* several vectors to be one vector.

```{r}
c(1,2,3,4,5)
```

Therefore, we can combine some single-entry vectors with multi-entry vectors to obtain the same vector as we did.

```{r}
c(1,2,c(3,4,5))
```

If we want to define a series of consecutive numbers with step one, `:` operator will do the trick.

```{r}
1:5
```

Or we can use `seq` function to produce a vector of a specific sequence, for example, one from 1 to 10 with step 2.

```{r}
seq(1,10,2)
```

Or another start from 3 with length 10.

```{r}
seq(3,length.out = 10)
```

There are many ways we can define numeric vectors. But we should always be careful when use `:` to define a range of numbers.

```{r}
1+1:5
```

As we can see, `1+1:5` does not mean a sequence from 2 to 5, but one from 2 to 6. It is because `:` has higher priority than `+`, which makes R evaluates `1:5` first and add 1 to each entry, yielding the sequence you see in the result.


#### Logical vector

In contrast with numeric vectors, a logical vector typically holds a group of `TRUE` of `FALSE` values. They are basically *yes* or *no* to denote the answers to a group of logical questions.

The simplest logical vector is `TRUE` or `FALSE` itself.

```{r}
TRUE
```

A more usual way to to obtain a logical vector is to ask logical questions. For example, we can ask R whether 1 is greater than 2.

```{r}
1 > 2
```

Its answer is correct. If we want to perform multiple comparisons at the same time, we can directly use numeric vectors.

```{r}
c(1,2) > 2
```

R interprets this expression as the element-wise comparisons between the two entries.

Moreover, we can compare two mutlti-entry numeric vectors as long as the length of the longer vector is a multiple of that of the shorter one.

```{r}
c(1,2) > c(2,1)
```

```{r}
c(2,3) > c(1,2,-1,3)
```

The computing mechanism is asking the following questions iteratively: `1>2?`, `2>3?`, `-1>2?`, `3>3?`. In other words, the shorter vector will rotate to finish all the comparisons for each entry in the longer vector.

#### Character vector

A character vector is a group of strings. Here a *character* does not mean literally a single letter or symbol in a language, but means a string. A character vector is a group of a number of strings. Both double-quotes and single-quotes can be used to define a character vector.

```{r}
"hello, world!"
```

```{r}
'hello, world!'
```

We can also use combine function `c` to construct a multi-entry character vector.

```{r}
c("Hello","World")
```

We can use `==` to tell whether two vectors have the same values, which applies to character vector too.

```{r}
c("Hello","World") == c('Hello','World')
```

The character vectors are equal because `"` and `'` both work.

```{r}
c("Hello","World") == "Hello, World"
```

he previous expression yields both `FALSE` because neither `"Hello"` nor `"World"` equals `"Hello, World"` as a whole.

#### Date vector


#### Named vector


#### Subsetting vectors

#### Obtaining the type of a vector

#### Converting vectors

#### Arithmetic operators for numeric/integer vectors


